Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-10-08 analysis/report/effectiveness_report.Rmd
simplify intro

The COVID-19 global pandemic has prompted the rapid development and delivery of vaccines to combat the disease. Following demonstration of high safety and efficacy against symptomatic and severe disease in phase-III randomised clinical trials (RCTs), two vaccines have been approved and widely administered as part of the national vaccination programme in the United Kingdom: the Pfizer-BioNTech BNT162b2 mRNA COVID-19 vaccine (*BNT162b2*) and the Oxford-AstraZeneca ChAdOx1 nCoV-19 vaccine (*ChAdOx1*). To date, there have been no RCTs that have directly compared these two vaccines to estimate the relative efficacy against COVID-19 infection and disease in the same cohort. The concurrent roll-out of BNT162b2 and ChAdOx1 within the same UK population provides an opportunity to emulate such a trial using observational data.

COVID-19 vaccination in the UK has been prioritised based on the risk of infection and subsequent severity of disease. Patient-facing health and social care workers (HCWs) were amongst the first groups eligible for vaccination due to the high occupational exposure to the SARS-CoV-2 virus, and many were vaccinated during the period where both vaccines were widely used (`r format(as.Date(gbl_vars$start_date_az), "%d %B %Y")` onwards). This study assessed the comparative effectiveness of one dose of ChAdOx1 with one dose of BNT162b2 in HCWs, using the OpenSAFELY-TPP database covering around 40% of England's population.

@@

Study participants were followed up for 14 weeks from the date of the first dose, or until the first of:

-   death or deregistration;
-   Second vaccine dose;
-   The study end date, `r format(as.Date(gbl_vars$end_date), "%d %B %Y")`.

>>>>

This study assessed the comparative effectiveness of one dose of ChAdOx1 with one dose of BNT162b2 in HCWs, using the OpenSAFELY-TPP database covering around 40% of England's population.

@@

Study participants were followed up for 20 weeks from the date of the first dose, or until the first of:

-   death or deregistration;
-   The study end date, `r format(as.Date(gbl_vars$end_date), "%d %B %Y")`.
